---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
## Install the required package with:
## install.packages("RSocrata")
## Reference: https://dev.socrata.com/foundry/data.medicare.gov/eqxu-aw4f

library("RSocrata")

# Reading in the "Dialysis Facility Compare"" data
dfc.df <- read.socrata(
  "https://data.medicare.gov/resource/eqxu-aw4f.json",
  app_token = "a2pVgaK9QKjxN5iNc4DLohtjI",
  email     = "shells.27@gmail.com",
  password  = "MCh@nge2018",
  stringsAsFactors = FALSE
)
```
# Reading in "ESRD QIP - Complete QIP Data - Payment Year 2018" data
```{r}
esrdqip.df <- read.socrata(
  "https://data.medicare.gov/resource/m26r-4ib8.json",
  app_token = "a2pVgaK9QKjxN5iNc4DLohtjI",
  email     = "shells.27@gmail.com",
  password  = "MCh@nge2018",
  stringsAsFactors = FALSE
)
```
# Reading in "Patient survey (ICH CAHPS)" data
```{r}
patsurvey.df <- read.socrata(
  "https://data.medicare.gov/resource/rza3-mnpj.json",
  app_token = "a2pVgaK9QKjxN5iNc4DLohtjI",
  email     = "shells.27@gmail.com",
  password  = "MCh@nge2018",
  stringsAsFactors = FALSE
)
```
# Patient utility function
```{r}

c <- c("10461")
facinfo <- function (c) {
#
# FUNCTION TO PROVIDE FACILITY ADDRESS, RATING INFORMATION & MAP 
#  
# INPUTS: 
#
# C - Character vector with one or more zipcode values
# 
# OUTPUTS: A dataframe with facility address, contact, network, and
# patient rating
# Load libraries
library(dplyr)
library(leaflet)
# Create empty list 'infolist'
infolist <-list()
# Create dataframe 'tmpzip' with filtered data corresponding to 'c'zip code values 
tmpzip <- geo_join %>% filter(Zip %in% c)
# For loop to perform functions on each row value of tmpzip
for (row in 1:nrow(tmpzip)){
# Create & populate 'infolist' elements from corresponding 'tmpzip' elements
  
infolist$Name <- tmpzip$Facility_Name
infolist$Address <- tmpzip$Address_Line_1
infolist$City <- tmpzip$City
infolist$State <- tmpzip$state
infolist$Contact <- tmpzip$Phone_Number
infolist$Network <- tmpzip$Network
infolist$Rating <- tmpzip$ptfacrate
infolist$Score <- tmpzip$perfcats}
# Create 'listout' with Adress, phone, Network, Rating, Score information for each facility
listout <- list(Address=paste(infolist$Name,infolist$Address,infolist$City,infolist$State,sep=","),
                Phone=infolist$Contact,Network=infolist$Network,
                "Patient Rating"=infolist$Rating,
                "Performance Score"=infolist$Score)
# Create output 'retdf' dataframe from 'listout' elements 
retdf <- data.frame (listout)
# Create Leaflet map 'locations' by using lat-long values for each facility
locations <- leaflet(tmpzip) %>% addTiles() %>% 
    addMarkers(~longitude,~latitude, popup=~Facility_Name,
               clusterOptions=markerClusterOptions())
# Create & populate final output list 'facinfoloc' elements with 'retdf' and 'locations'
facinfoloc <- list("Facility Information"=retdf,Map=locations)
# Provide dataframe and map outputs
return(facinfoloc)
}
```
```{r}
#facinfo(c)
```

```{r}
```
# Create dataframe with selected DFC variables
```{r}
library(dplyr)
dfc <- dfc.df %>% select(provider_number,facility_name,network,address_line_1,
                         city,state,zip,chain_owned,five_star,
                         X_of_dialysis_stations,mortality_rate_facility,
                         readmission_rate_facility,
                         standardized_hospitalization_ratio,
                         standardized_readmission_ratio,
                         standard_infection_ratio)
```
# Create dataframe with selected ESRDQIP variables
```{r}
library(dplyr)
esrdqip <- esrdqip.df %>% select(cms_certification_number_ccn,
                                 strr_measure_score,total_performance_score,
                                 nhsn_bsi_measure_score,
                                 kt_v_dialysis_adequacy_combined_measure_score,
                                 anemia_management_measure_score,
                                 vascular_access_combined_measure_score,
                                 mineral_metabolism_measure_score)

```
# Create dataframe with selected Patient survey variables
```{r}
patsurvey <- patsurvey.df %>% select(provider_number, starts_with("top_box"))
names(patsurvey) <- gsub("top_box_percent_of_patients_","",names(patsurvey))
```
# Reading in Dialysis Facility Report file
```{r}
library(readr)
setwd("~/INFO 550/Project/Files")
dfr <- read_delim("DFR_Data_FY2017.csv", delim = ",")

# Selecting demographic, ESRD cause, Transplant variables from DFR
fac_demo <- select(dfr,provfs,rac1y4_f,
                   rac2y4_f,rac3y4_f,rac4y4_f,rac5y4_f,eth1y4_f,
                   eth2y4_f,eth3y4_f,sexy4_f,agey4_f,dis1y4_f,dis2y4_f,
                   dis3y4_f,dis4y4_f,rdsallty4_f,txally4_f)

# Create data frame from DFR variables
fac_demo1 <- data.frame(fac_demo)
```
# Join data frames
```{r}
# DFC + DFR data
df1 <- left_join (dfc,fac_demo1, by=c("provider_number"="provfs"))
# ESRDQIP + Patsurvey data
df2 <- left_join(patsurvey,esrdqip,
                 by=c("provider_number"="cms_certification_number_ccn"))
# DFC + DFR + ESRDQIP + Patsurvey data
allfacdata <- left_join(df1,df2,by=c("provider_number"="provider_number"))

# Conversion of rate & measure variables to numeric
# Columns 9 through 44 are rate/ measure variables which will be converted to numeric, columns 1 though 8 are retained as character variables)
allfac <- data.frame(allfacdata[,1:8], sapply(allfacdata[,9:44], function(x) as.numeric(x)))
```
# Adding zipcode xy coordinates 
```{r}
library(dplyr)
# Install "zipcode" package
library(zipcode)
data("zipcode")
# Select columns from zipcode 
zipcoord <- zipcode %>% select(zip,longitude,latitude)
# Join zip code data
geo_join <- left_join(allfac, zipcoord, by=c("zip"="zip"))
```
# Using SQLite to import CKD prevalence data
```{r}
# Set working directory to location of database
setwd("C:/Users/shail")
# load libraries
library(DBI)
library(RSQLite)

con <- dbConnect(RSQLite::SQLite(),dbname="CKD_Prevalence.db")
# Show tables in database
dbListTables(con)
# Show types of prevalence measures
dbGetQuery(con,"select distinct DataValueTypeID from CKD_prev")
# Get Crude prevalence values for each state into a dataframe
ckd_prev <- dbGetQuery(con,"select LocationAbbr,avg(DataValue) from CKD_prev 
                       where DataValueTypeID='CrdPrev' and 
                       Question like '%kidney%' and 
                       YearStart='2016' group by LocationAbbr")
dbDisconnect(con)
ckd_prev
```
# Join Prevalence data
```{r}
library(dplyr)
alldata <- left_join(geo_join,ckd_prev,by=c("state"="LocationAbbr"))
```
# Creating categories in continuous variables
```{r}
# Variable 'perfcats' for Facility performance score categories
alldata$perfcats <- cut(alldata$total_performance_score,
                         breaks = quantile(alldata$total_performance_score,na.rm = TRUE),
                         labels=c("Poor","Fair","Good","Very good"),include.lowest=TRUE)

# Variable 'facrating' for patient's rating of Dialysis facilities
alldata$facrating <- cut(alldata$rating_of_the_dialysis_facility,
                         breaks = quantile(alldata$rating_of_the_dialysis_facility,na.rm = TRUE),
                         labels=c("Poor","Fair","Good","Very good"),
                         include.lowest=TRUE)

# Variable 'stations' for number of dialysis stations categories
alldata$stations <- cut(alldata$X_of_dialysis_stations,breaks=c(0,mean(alldata$X_of_dialysis_stations),max(alldata$X_of_dialysis_stations)),c("up to 17","17 to 80"))

# Make 'five_star' a factor 
alldata$five_star <- factor(alldata$five_star)

```
# Exploratory analysis
```{r}
library(ggplot2)
# Number of facilities in networks
# Networks 6,14,9 have top 3 highest number of facilities
alldata %>% group_by(network) %>% summarize(total=n()) %>% arrange(desc(total))
# Number of facilities in networks, by chain status
# Most facilities are chain owned
alldata %>% ggplot(aes(x=network)) + 
  geom_bar(aes(fill=chain_owned),stat="count") + 
  ggtitle("Network facilities by chain status")
```
# Mortality rate in facilities
```{r}
# Most facilities are chain owned, and Mortality is higher in chain-ownwd facilities 
alldata %>% ggplot(aes(x=mortality_rate_facility)) + geom_histogram() + 
  ggtitle("Mortality Rates in facilities")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=readmission_rate_facility)) + geom_point()+geom_smooth(method="lm") + ggtitle("Mortality rate vs readmission rate")
ggplot(data = alldata, 
       aes(x = alldata$perfcats, y = alldata$mortality_rate_facility)) + 
    geom_boxplot()
ggplot(data = alldata, 
       aes(x = alldata$five_star, y = alldata$mortality_rate_facility)) + 
    geom_boxplot()
alldata %>% ggplot(aes(x=mortality_rate_facility,y=readmission_rate_facility,color=fac5star)) + geom_point() + ggtitle("Mortality rate vs readmission rate")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=readmission_rate_facility,color=chain_owned)) + geom_point() + ggtitle("Mortality rate vs readmission rate") + facet_wrap(~five_star)

# Filtering higher mortality cases
alldata %>% filter(mortality_rate_facility >= 40) %>% select(chain_owned,network,state)
alldata %>% filter(mortality_rate_facility >= 40) %>% group_by(chain_owned) %>% summarize(n())
```
# CKD prevalence
```{r}
# Summary of prevalence of Chronic Kidney Disease within networks
# Network 10 has highest prevalence
alldata %>% group_by(network) %>% summarize(meanprev=mean(`avg(DataValue)`)) %>% arrange(desc(meanprev))
# Plotting prevalence of CKD in networks (no values for network 17-
# Northern California, Hawaii, Guam, Mariana Islands, and American Samoa- no data
alldata %>% group_by(network) %>% summarize(meanprev=mean(`avg(DataValue)`)) %>% ggplot(aes(x=network,y= meanprev)) + geom_bar(stat = "identity") + 
  ggtitle("Mean Chronic Kidney Disease (CKD) prevalence in networks")
```
# Facility performance scores
```{r}
alldata %>% ggplot(aes(x=total_performance_score)) + geom_histogram() + 
  ggtitle("Total perf score in facilities")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=total_performance_score)) + geom_point()+geom_smooth(method="lm") + ggtitle("Mortality rate vs Total perf score")
ggplot(data = alldata, 
       aes(x = alldata$perfcats, y = alldata$total_performance_score)) + 
    geom_boxplot()
ggplot(data = alldata, 
       aes(x = alldata$fac5star, y = alldata$total_performance_score)) + 
    geom_boxplot()
alldata %>% ggplot(aes(x=mortality_rate_facility,y=total_performance_score,color=fac5star)) + geom_point() + ggtitle("Mortality rate vs total perf score")

alldata %>% group_by(network) %>% summarize(meanscore=mean(total_performance_score,na.rm = TRUE)) %>% arrange(desc(meanscore))
# Plotting prevalence of CKD in networks (no values for network 17-
# Northern California, Hawaii, Guam, Mariana Islands, and American Samoa- no data
alldata %>% group_by(network) %>% summarize(meanscore=mean(total_performance_score,na.rm = TRUE)) %>% ggplot(aes(x=network,y= meanscore)) + geom_bar(stat = "identity") + 
  ggtitle("Mean facility performance score in networks")
```
# Examining 'poor' performing networks
```{r}
# Top 10 states with the highest number of 'poor' performing facilities
alldata %>% filter(perfcats == "Poor") %>% group_by(state) %>% 
    summarize(total=n()) %>% arrange(desc(total)) %>% head(.,10)
# Fewer faciities with higher mortality & readmission rates in good-very good performance
alldata %>% ggplot(aes(x=mortality_rate_facility)) + geom_histogram() + facet_wrap(~perfcats) + ggtitle("Mortality Rates by facility performance scores")
alldata %>% ggplot(aes(x=readmission_rate_facility)) + geom_histogram() + facet_wrap(~perfcats) + ggtitle("Readmission Rates by facility performance scores")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=standardized_hospitalization_ratio)) + geom_point()+geom_smooth(method="lm") + ggtitle("Mortality rate vs SHR")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=standard_infection_ratio)) + geom_point()+geom_smooth(method="lm") + ggtitle("Mortality rate vs SIR")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=standardized_readmission_ratio)) + geom_point()+geom_smooth(method="lm") + ggtitle("Mortality rate vs SRR")
alldata %>% ggplot(aes(x=mortality_rate_facility,y=standardized_readmission_ratio)) + geom_point()+geom_smooth(method="lm") + facet_wrap(~perfcats) + ggtitle("Mortality rate vs SRR by performance scores")
```
# Five star ratings
```{r}
# Make five_star variable a factor
# alldata$five_star <- factor(alldata$five_star)
# Majority of facilities are 3,4,5 star rated, 698 are 1 or 2 star rated: FL, TX, GA, CA, NY, OH, IL, TN, LA, MI 
summary(alldata$five_star)
alldata %>% ggplot(aes(x=five_star)) + geom_bar(stat = "count")
star <- c("1","2")
alldata %>% filter(five_star %in% star) %>% group_by(state) %>% summarize(total=n()) %>% arrange(desc(total)) %>% head(.,10)
# Histogram shows that even though fwewer facilities have 1 & 2 srat ratings, the mortality in these facilities is much higher (40)
alldata %>% ggplot(aes(x=mortality_rate_facility)) + geom_histogram() + facet_wrap(~five_star) + ggtitle("Mortality Rates by Star Rating")

```
# Transplants
```{r}
alldata %>% group_by(network) %>% summarize(meantx=mean(rdsallty4_f,na.rm = TRUE)) %>% ggplot(aes(x=network,y= meantx)) + geom_bar(stat = "identity") + 
  ggtitle("Mean kidney transplants in networks")
alldata %>% ggplot(aes(x=rdsallty4_f)) + geom_histogram() + facet_wrap(~five_star) + ggtitle("Transplants by Star Rating")
alldata %>% ggplot(aes(x=rdsallty4_f)) + geom_histogram() + facet_wrap(~perfcats) + ggtitle("Transplants by performance score")
alldata %>% ggplot(aes(x=rdsallty4_f)) + geom_histogram() + facet_wrap(~stations) + ggtitle("Transplants by number of dialysis stations")
alldata %>% ggplot(aes(x=rdsallty4_f,y=X_of_dialysis_stations)) + geom_point()+geom_smooth(method="lm") + ggtitle("Transplants vs no. of dialysis stations")
```
# Mapping
```{r}
library(ggmap)
library(ggplot2)
usbasemap <- get_map(location = 'United States', zoom= 4, maptype = "terrain", source='google', color='color')
ggmap(usbasemap)

```
# Mapping poor performing facilities
```{r}
# Filter cases with "poor" score
poorperf <- alldata %>% filter(perfcats == "Poor")
geopoorperf <- ggmap(usbasemap) + geom_point(aes(x=longitude,y=latitude),data=poorperf, na.rm = T, color="red", alpha=0.3,size=1) + ggtitle("Facilities with lowest performance scores")
# Filter cases with 1 & 2 star rating
lowstar <- alldata %>% filter(five_star %in% star)
geolowstar <- ggmap(usbasemap) + geom_point(aes(x=longitude,y=latitude),data=lowstar, na.rm = T, color="blue", alpha=0.3,size=1) + ggtitle("Facilities with 1 & 2 star ratings")
```
# answering the question about geographical distribution of poor performing states
```{r}
# Mapping top 10 poor performance & 1-2 star states
states <- map_data("state")
poorstates <- c("florida","texas","georgia","california","new york","ohio","illinois","tennessee","louisiana","michigan","pennsylvania","maryland")
poorstates1 <- states %>% filter (region %in% poorstates)
ggmap(usbasemap) + geom_polygon(data = poorstates1, aes(x=long, y=lat, group = group), fill = NA, color = "red")

ggmap(usbasemap) + geom_polygon(data = poorstates1, aes(x=long, y=lat, group = group), fill = "yellow", color = "red")
```
# Mapping prevalence
```{r}
prev <- ggmap(usbasemap) + geom_point(aes(x=longitude, y=latitude, color=`avg(DataValue)`), data=alldata, alpha=.5, na.rm = T)  + scale_color_gradient(low="yellow", high="blue")

```
# Cluster analysis
```{r}
# Create data frame "allfac.num1" with variables for cluster analysis
# Filtering by mortality value outliers based on the distribution of Mortality
allfac.num1 <- alldata %>% filter(mortality_rate_facility >= 5 & mortality_rate_facility <= 30) %>% select(provider_number,network,chain_owned,five_star,perfcats,
                                 mortality_rate_facility,readmission_rate_facility,
                                 strr_measure_score,standardized_hospitalization_ratio,
                                 standardized_readmission_ratio,total_performance_score,
                                 nhsn_bsi_measure_score,anemia_management_measure_score,
                                 kt_v_dialysis_adequacy_combined_measure_score,
                                 vascular_access_combined_measure_score,
                                 mineral_metabolism_measure_score,X_of_dialysis_stations)
                             
# Selecting complete cases with numeric variables
allfacnum1 <- allfac.num1 %>% select_if(is.numeric)
```
# other possible filter options
```{r}
alldata %>% filter(!five_star==1) %>% group_by(perfcats) %>% summarize(meanMR=mean(total_performance_score,na.rm = TRUE))

alldata %>% filter(!five_star==1) %>% 
  summarize(meanPS=mean(total_performance_score,na.rm = TRUE))
alldata %>% filter(!five_star==1) %>% ggplot(aes(x = perfcats, y = total_performance_score)) + geom_boxplot()

alldata %>% filter(!five_star==1) %>% 
  summarize(meanMR=mean(mortality_rate_facility,na.rm = TRUE))
alldata %>% filter(!five_star==1) %>% ggplot(aes(x = perfcats, y = mortality_rate_facility)) + geom_boxplot()
```
# Cluster analysis
```{r}
library(NbClust)
# Scaling all variables
scaled.allfac <- scale(allfacnum1)
# Calculating distance between scaled variables
dist.allfac <- dist(scaled.allfac)
allfac_clust <- hclust(dist.allfac,method = "complete")
plot(allfac_clust,cex=0.1)
# using different heights on y axis to see optimal cluster number
rect.hclust(allfac_clust, h=12, border="red")
# This shows 2 clusters
# using number of clusters
plot(allfac_clust,cex=0.1)
rect.hclust(allfac_clust, k=5, border="red")
```
# Trying to investigate
```{r}
g45 <- cutree(allfac_clust, k = c(4,5))
table(grp4 = g45[,"4"], grp5 = g45[,"5"])
# clusters 2 thru 5
g23 <- cutree(allfac_clust,k=c(2,3))
table(grp2 = g23[,"2"], grp3 = g23[,"3"])
```

# using NBclust "complete" method
```{r}
res1 <- NbClust(scaled.allfac,distance="euclidean",
               min.nc=2,max.nc=5,method="complete",
               index="all")
``` 
# Using NBClust "ward.d2" method
```{r}
res2 <- NbClust(scaled.allfac2,distance="euclidean",min.nc=2,
                max.nc=5,method="ward.D2",index="silhouette")
res2$Best.nc
```

```{r}
res3 <- NbClust(scaled.allfac,distance="euclidean",
               min.nc=2,max.nc=5,method="kmeans",
               index="all")
```

# Looking at 5 clusters, assuming that it will follow 5 star rating distribution
```{r}
library(ggplot2)
numclust <- 5
allfac_5 <- cutree(allfac_clust,k=numclust)
clust_labs <- factor(allfac_5,labels=1:numclust)
allfac.num1$labs <- clust_labs
title <- paste(numclust,"Clusters",sep=" ")
# Plotting mortality $ readmission rates for 5 clusters
ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$five_star) + ggtitle(title)

ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$chain_owned)
# Check the fit
table(allfac.num1$five_star,allfac.num1$labs)
```
Looking at 4 clusters, assuming that it will follow performance score categories
```{r}
numclust <- 4
allfac_4 <- cutree(allfac_clust,k=numclust)
clust_labs <- factor(allfac_4,labels=1:numclust)
allfac.num1$labs <- clust_labs
# title <- paste(numclust,"Clusters",sep=" ")
# Plotting mortality $ readmission rates for 4 clusters
ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=allfac.num1$labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$perfcats)

ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$chain_owned)
# Check the fit
table(allfac.num1$perfcats,allfac.num1$labs)
```
# Lookign at 2 clusters
```{r}
numclust <- 2
allfac_2 <- cutree(allfac_clust,k=numclust)
clust_labs <- factor(allfac_2,labels=1:numclust)
allfac.num1$labs <- clust_labs
# title <- paste(numclust,"Clusters",sep=" ")
# Plotting mortality $ readmission rates for 2 clusters
ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=allfac.num1$labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$perfcats)

ggplot(allfac.num1,aes(x=allfac.num1$mortality_rate_facility,
                     y=allfac.num1$readmission_rate_facility,fill=labs)) +
  geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num1$chain_owned)
# Check the fit
table(allfac.num1$chain_owned,allfac.num1$labs)
```
# kmeans clustering
```{r}
# Create 3 clusters
# numclust <- 3
allfac.num2 <- alldata %>%  filter(complete.cases(.)) %>% filter(mortality_rate_facility >= 5 & mortality_rate_facility <= 30) %>% select(provider_number,network,chain_owned,five_star,perfcats,
                                 mortality_rate_facility,readmission_rate_facility,
                                 strr_measure_score,standardized_hospitalization_ratio,
                                 standardized_readmission_ratio,total_performance_score,
                                 nhsn_bsi_measure_score,anemia_management_measure_score,
                                 kt_v_dialysis_adequacy_combined_measure_score,
                                 vascular_access_combined_measure_score,
                                 mineral_metabolism_measure_score,X_of_dialysis_stations,
                                 rdsallty4_f)

# Selecting complete cases for kmeans clustering
allfacnum2 <- allfac.num2 %>% select_if(is.numeric)
scaled.allfac2 <- scale(allfacnum2)
# performing kmeans clustering

set.seed(1)
kmres3 <- kmeans(scaled.allfac2,2)
#table(allfac.num2$perfcats,kmres1$cluster)

labs <- factor(kmres3$cluster,labels=1:2)
df <- data.frame(scaled.allfac2) 
centers <- as.data.frame(kmres3$centers)
title <- "K-Means cluster with Centroids" 
plot(df$mortality_rate_facility,
     df$readmission_rate_facility,
     col=kmres3$cluster,pch=25)
points(kmres3$centers[,c(1,2)],col=1:3,pch=19,cex=4)
grid()
ggplot(df,aes(x=df$mortality_rate_facility,
              y=df$readmission_rate_facility,
              color=labs)) + geom_point() 

ggplot(df,aes(x=df$Mortality_Rate_.Facility.,
              y=df$Readmission_Rate_.Facility.,
              color=labs)) + geom_point() + facet_wrap(~df$Five_Star)
allfac.num2$labs <- labs
ggplot(allfac.num2,aes(x=allfac.num2$mortality_rate_facility,
                     y=allfac.num2$readmission_rate_facility,fill=allfac.num2$labs)) + geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num2$perfcats)
ggplot(allfac.num2,aes(x=allfac.num2$mortality_rate_facility,
                     y=allfac.num2$readmission_rate_facility,fill=allfac.num2$labs)) + geom_point(pch=23,size=1.0) + facet_wrap(~allfac.num2$five_star)


allfac.num2 %>% group_by(labs) %>% summarize(meanMR=mean(mortality_rate_facility))
allfac.num2 %>% group_by(labs) %>% summarize(meanMR=mean(total_performance_score))
allfac.num2 %>% group_by(labs) %>% summarize(meanMR=mean(X_of_dialysis_stations))
allfac.num2 %>% group_by(labs) %>% summarize(meanMR=mean(rdsallty4_f))



```
# Regression analysis
```{r}
# Create data frame "allfac.mod" with variables for regression analysis
allfac.mod <- alldata %>%  filter(complete.cases(.)) %>% filter(mortality_rate_facility >= 5 & mortality_rate_facility <= 30) %>% select(provider_number,network,chain_owned,five_star,perfcats, mortality_rate_facility,readmission_rate_facility, strr_measure_score,standardized_hospitalization_ratio, standardized_readmission_ratio,total_performance_score, nhsn_bsi_measure_score,anemia_management_measure_score, kt_v_dialysis_adequacy_combined_measure_score,vascular_access_combined_measure_score,mineral_metabolism_measure_score,X_of_dialysis_stations,  rdsallty4_f,`avg(DataValue)`,rac1y4_f,rac2y4_f,rac3y4_f,rac4y4_f,rac5y4_f,eth1y4_f,eth2y4_f,eth3y4_f,dis1y4_f,dis2y4_f,dis3y4_f,dis4y4_f,rdsallty4_f)                                                                              
# Selecting numeric cases
allfacnum3 <- allfac.mod %>% filter(complete.cases(.)) %>% select_if(is.numeric)
```
# Correlations
```{r}
library(corrplot)
cor.allfacrates <- cor(allfacnum2)
corrplot(cor.allfacrates,tl.cex=0.5)
```
#Using steps
```{r}
allfac_MR <- lm(mortality_rate_facility~.,data=allfacnum2)
allfac_steps1 <- step(allfac_MR,direction="backward",data=allfacnum2)
summary(allfac_steps1)

allfac_tx <- lm(rdsallty4_f~., data=allfacnum2)
allfac_steps2 <- step(allfac_tx,direction="backward",data=allfacnum2)
summary(allfac_steps2)

allfac_ps <- lm(total_performance_score~., data=allfacnum2)
allfac_steps3 <- step(allfac_ps,direction="backward",data=allfacnum2)
summary(allfac_steps3)

```
# Calculating correlations
```{r}
# Function 'corfun' to calculate correlations
# Inputs: df=dataframe, a=variable1, b=variable2
corfun <- function(df=allfacnum3,a,b){df %>% summarize(N=n(),r=cor(a,b))}
corfun(a=allfacnum3$mortality_rate_facility,b=allfacnum3$five_star)
corfun(a=allfacnum3$mortality_rate_facility,b=allfacnum3$readmission_rate_facility)
```

```{r}
# Filtering out higher mortality outliers 
allfacnum3 <- allfacnum2 %>% filter(mortality_rate_facility < 30)
allfacnum4 <- allfacnum3 %>% filter(complete.cases(.)) 
allfac_MR <- lm(rdsallty4_f~.,data=allfacnum4)
allfac_steps1 <- step(allfac_MR,direction="backward",data=allfacnum4)
summary(allfac_steps1)
```
# Modeling total performance scores
```{r}
# Consult plot, total performance score & five star are correlated
corfun(a=allfacnum3$total_performance_score,b=allfacnum3$five_star)
# Creating a model for total performance score as dependent variabe, five_star as a predictor
mod <- lm(total_performance_score ~ five_star, data=allfacnum3)
summary(mod)
```
```{r}
# Model 1: Adding Transfusion score
corfun(a=allfacnum3$total_performance_score,b=allfacnum3$strr_measure_score)
mod1 <- lm(total_performance_score ~ five_star + strr_measure_score, data=allfacnum3)
summary(mod1)
```
```{r}
# Model 2: Adding Infection measure score
corfun(a=allfacnum3$total_performance_score,b=allfacnum3$standardized_hospitalization_ratio)
mod2 <- lm(total_performance_score ~ five_star + strr_measure_score + nhsn_bsi_measure_score, data=allfacnum3)
summary(mod2)
```
```{r}
# Model 3: Adding dialysis adequacy measure score
mod3 <- lm(total_performance_score ~ five_star + strr_measure_score + nhsn_bsi_measure_score + kt_v_dialysis_adequacy_combined_measure_score, data=allfacnum3)
summary(mod3)
```
```{r}
# Model 4: Adding vascular access score
mod4 <- lm(total_performance_score ~ five_star + strr_measure_score + nhsn_bsi_measure_score + kt_v_dialysis_adequacy_combined_measure_score + vascular_access_combined_measure_score, data=allfacnum3)
summary(mod4)
```
```{r}
#Model 5: Adding readmission_rate
mod5 <- lm(total_performance_score ~ five_star + strr_measure_score + nhsn_bsi_measure_score + kt_v_dialysis_adequacy_combined_measure_score + vascular_access_combined_measure_score + readmission_rate_facility, data=allfacnum3)
summary(mod5) 
```
```{r}
# Regression plots 
hist(mod5$residuals)
qqnorm(mod5$residuals)
qqline(mod5$residuals)
plot(mod5$fitted.values,mod5$residuals)
```
```{r}
plot(mod5$fitted.values,mod5$residuals)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
